---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
The following code shows how the data was imported.
```{r data import}
data <- read.csv('activity.csv')
```

## Histogram showing the total number of steps taken everyday
The following code was used to determine the total number of steps per day
```{r histogram}
agg <- aggregate(steps~date,data,sum)
hist(agg$steps)
```

## What is mean total number of steps taken per day?
```{r}
meansteps <- mean(agg$steps)
mediansteps <- median(agg$steps)
```
The mean number of steps per day is `r format(meansteps, scientific=F)` and the median number of steps is `r format(mediansteps, scientific=F)`.  

## What is the average daily activity pattern?
The following code is used to determine the average number of steps per 5-min interval and plots the resulting data
```{r}
dayagg <- aggregate(steps~interval,data,mean)
plot(dayagg$interval,dayagg$steps,type = "l",xlab='Time of day',ylab='Average number of steps', main='Average daily number of steps per 5-min interval')
```


## Imputing missing values
All missing values were imputed using the average number of steps for that particular 5-min interval.
```{r}
data[is.na(data)] = 0
hist(agg$steps)
```


## Are there differences in activity patterns between weekdays and weekends?
